Large-scale harmonic patterns clustering

### 2010-03-17 Paper/Paper.tex
better lle pic
results added

% RESULTS
% 200codes, 2 bars, pSize=16, maxener, True, False, not scaled = 
% 200codes, 2 bars, pSize=8, maxener, True, False, not scaled  = 0.042432
% 200codes, 1 bars, pSize=4, maxener, True, False, not scaled  = 
% 200codes, 7 beats, pSize=7, maxener, True, False, not scaled = 
% 200codes, 5 beats, pSize=5, maxener, True, False, not scaled = 
% 200codes, 3 beats, pSize=3, maxener, True, False, not scaled = 
\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
size & avg. dist \\ \hline \hline
1 bar (4) & $0.036722$\\
2 bars (8) & $0.044301$\\
2 bars (12) & $0.043583$\\
2 bars (16) & $0.044086$ \\ \hline
3 beats & $0.032688$\\
5 beats & $0.040858$\\
7 beats & $0.045515$\\ \hline
\end{tabular}
\end{center}
\caption{{Encoding score for different pattern sizes. We can select the
size of the patterns based on bars. In this case, we put the actual size
of the pattern in parentheses. If the pattern size is based on beats, the
size is the number of beats. Results are on the uspop dataset, not seen
during training.}}
\label{tab:psize}
\end{table}

@@

\iffalse
\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
size & $5$K & $10$K & $50$K & $100$K & $500$K & $2$M  \\ \hline
distortion & $$ & $0.143$ & $0.142$ & $0.142$ & $0.142$ & $$\\ \hline
\end{tabular}
\end{center}
\caption{{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $10$ thousands to $2$ millions. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.}}
\label{tab:datasize}
\end{table}
\fi
% RESULTS:    
% 1bar s4     avg_distOLD    avg_dist
% 1K          0.150370       0.041941
% 5K          0.145327       0.038449
% 10K         0.143567       0.036892
% 50K         0.142257       0.036722
% 100K        0.142195       0.035973
% 250K        0.141796       0.035910
% 500K        0.142081       0.035904
% 1M          0.142118
% 2M          0.141596
% 1bar s4 first X samples
% 1K          0.157142       
% 5K          0.150045
% 10K         0.148357
% 50K         0.146069
% 100K        0.145765
% 250K        0.145819
% 500K        0.145772
% 1M          0.145924
% 2M          0.146065       
% 0bar s4 (and test set same, we could do 1bar s4 in test set...)
% 1K          0.155474       0.042596
% 5K          0.149619       0.038971
% 10K         0.148056       0.038114
% 50K         0.146328       0.037181
% 100K        0.146004       0.037055
% 250K        0.146024       0.037014
% 500K        0.145962       0.037004
% 1M          0.145873
% 2M          0.145955
% 2bar s8     
% 1K          0.171300       0.049282
% 5K          0.165960       0.046441
% 10K         0.165063       0.045507
% 50K         0.162439       0.044301
% 100K        0.161588       0.044183
% 250K        0.161910       0.043896
% 500K        0.161233       0.043906
% 1M          0.161057
% 2M          0.161068

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes, which is sufficient
according to Figure \ref{fig:sizes}.}}
\label{tab:cbsize}
\end{table}
% RESULTS:      avg_distsOLD    avg_dist
% code 1        0.195939        0.066079
% code 10       0.161812        0.045690
% code 50       0.147472        0.038456
% code 100      0.142194        0.036725
% code 200      0.137548        0.033923
% code 500      0.131211        0.030973
% REDONE WITH FIX NUMBER OF FEATURES - 500K (new correct dist)
% code 1        
% code 10       0.045579
% code 50       0.038302
% code 100      
% code 200      
% code 500

@@

@@

\section{Links with NMF}\label{sec:nmf}
In this section we discuss links with non-negative matrix factorization
\cite{Lee2000} (NMF), another method to build a codebook representing some data.
NMF finds two matrices $H$ and $W$ that approximate some data $D$ (one
sample per line) by
\begin{eqnarray}
D \approx W^{m \times k} H^{k \times n}
\end{eqnarray}
where $\epsilon$ is some noise and $W$ and $H$ only have non-negative 
elements. If $W$ is $\#samples \times k$, $k$ is the codebook size.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
size & avg. dist \\ \hline \hline
1 bar (4) & $0.036722$\\
2 bars (8) & $0.044301$\\
2 bars (12) & $0.043583$\\
2 bars (16) & $0.044086$ \\ \hline
3 beats & $0.032688$\\
5 beats & $0.040858$\\
7 beats & $0.045515$\\ \hline
\end{tabular}
\end{center}
\caption{{Encoding score for different pattern sizes. We can select the
size of the patterns based on bars. In this case, we put the actual size
of the pattern in parentheses. If the pattern size is based on beats, the
size is the number of beats. Results are on the uspop dataset, not seen
during training.}}
\label{tab:psize}
\end{table}
% RESULTS
% 200codes, 2 bars, pSize=16, maxener, True, False, not scaled = 
% 200codes, 2 bars, pSize=8, maxener, True, False, not scaled  = 0.042432
% 200codes, 1 bars, pSize=4, maxener, True, False, not scaled  = 
% 200codes, 7 beats, pSize=7, maxener, True, False, not scaled = 
% 200codes, 5 beats, pSize=5, maxener, True, False, not scaled = 
% 200codes, 3 beats, pSize=3, maxener, True, False, not scaled = 
% NEW STUFF - experiment set 7, 100 codes! 
% 2 beats 0 bars       0.025346
% 4 beats 0 bars       0.037181
% 6 beats 0 bars       0.043237
% 8 beats 0 bars       0.046832
% 9 beats 0 bars       0.048579
% 10 beats 0 bars      0.049530
% 11 beats 0 bars      0.050717
% 12 beats 0 bars      0.052020

@@

\iffalse
\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
size & $5$K & $10$K & $50$K & $100$K & $500$K & $2$M  \\ \hline
distortion & $$ & $0.143$ & $0.142$ & $0.142$ & $0.142$ & $$\\ \hline
\end{tabular}
\end{center}
\caption{{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $10$ thousands to $2$ millions. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.}}
\label{tab:datasize}
\end{table}
\fi
% RESULTS:    
% 1bar s4     avg_distOLD    avg_dist
% 0                          0.052247
% 1K          0.150370       0.041941
% 5K          0.145327       0.038449
% 10K         0.143567       0.036892
% 50K         0.142257       0.036722
% 100K        0.142195       0.035973
% 250K        0.141796       0.035910
% 500K        0.142081       0.035904
% 1M          0.142118
% 2M          0.141596
% 1bar s4 first X samples
% 0
% 1K          0.157142       0.049282
% 5K          0.150045       0.046441
% 10K         0.148357       0.045507
% 50K         0.146069       0.044301
% 100K        0.145765       0.044183
% 250K        0.145819       0.043896
% 500K        0.145772       0.043906
% 1M          0.145924       
% 2M          0.146065       
% 0bar s4 (and test set same, we could do 1bar s4 in test set...)
% 0
% 1K          0.155474       0.042596
% 5K          0.149619       0.038971
% 10K         0.148056       0.038114
% 50K         0.146328       0.037181
% 100K        0.146004       0.037055
% 250K        0.146024       0.037014
% 500K        0.145962       0.037004
% 1M          0.145873
% 2M          0.145955
% 2bar s8
% 0                          0.066864179424
% 1K          0.171300       0.049282
% 5K          0.165960       0.046441
% 10K         0.165063       0.045507
% 50K         0.162439       0.044301
% 100K        0.161588       0.044183
% 250K        0.161910       0.043896
% 500K        0.161233       0.043906
% 1M          0.161057
% 2M          0.161068

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes, which is sufficient
according to Figure \ref{fig:sizes}.}}
\label{tab:cbsize}
\end{table}
% RESULTS:      avg_distsOLD    avg_dist
% code 1        0.195939        0.066079
% code 10       0.161812        0.045690
% code 50       0.147472        0.038456
% code 100      0.142194        0.036725
% code 200      0.137548        0.033923
% code 500      0.131211        0.030973
% REDONE WITH FIX NUMBER OF FEATURES - 500K (new correct dist)
% code 1        
% code 10       0.045579
% code 50       0.038302
% code 100      0.035904
% code 200      
% code 500

@@

\subsection{Bar offset}
We study how great are patterns based on bars by playing with an offset.
The offset can be $0$ (normal case) or a quarter of bar, half a bar, and
three quarters of a bar.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
offset & avg. dist \\ \hline \hline
$0$ & $$ \\
$.25$ & $0.037130$ \\
$.50$ & $0.037241$ \\
$.75$ & $0.037337$ \\ \hline
\end{tabular}
\end{center}
\caption{{Results with different offset. Always $100$ codes.
\label{tab:offset}}}
\end{table}
% RESULTS             avg_results
% 0 offset            0.036722 (to be confirmed by set8exp0)
% .25 ofset           0.037130
% .50 ofset           0.037241
% .75 ofset           0.037337
% RESULTS FOR PARTIALBAR TOO
% 0 off .25 part      0.046304
% .25 off .25 part    0.044950
% .50 off .25 part    0.044395
% .75 off .25 part    0.044473

@@

\section{Links with NMF TO BE REMOVED}\label{sec:nmf}
In this section we discuss links with non-negative matrix factorization
\cite{Lee2000} (NMF), another method to build a codebook representing some data.
NMF finds two matrices $H$ and $W$ that approximate some data $D$ (one
sample per line) by
\begin{eqnarray}
D \approx W^{m \times k} H^{k \times n}
\end{eqnarray}
where $\epsilon$ is some noise and $W$ and $H$ only have non-negative 
elements. If $W$ is $\#samples \times k$, $k$ is the codebook size.
